Concurrent, Parallel Garbage Collection in Linear Time

### 2016-06-01 finaletd/mainintroduction.tex
changes

The amount static memory used is computed at the compilation phase and objects allocated in static memory is never deleted. Stack memory is used to manage function calls and the allocation of objects in a function's scope. So the size of the stack memory required for the execution cannot be computed at compilation time. Stack memory is filled from the lower address of memory and heap memory is filled with the higher address of the memory. When two kinds of memory meet, the program usually crashes.

Stack memory is the memory of all objects that are actively in use or will be used in the near future. Heap memory is the memory of all objects whose scope is unknown to the program. Developers control the lifetime of the objects in the heap memory and delete them when it is no longer used. Memory management is the term used to describe heap memory management. Developers write a program that creates the objects in the heap memory and deletes them when it is of no use. The developer managed memory is referred as manual memory management.

>>>>

The amount of static memory used is computed at the compilation phase and objects allocated in static memory is never deleted. Stack memory is used to manage function calls and the allocation of objects in a function's scope. So the size of the stack memory required for the execution cannot be computed at compilation time. Stack memory is filled from the lower address of memory and heap memory is filled with the higher address of the memory. When two kinds of memory meet, the program usually crashes.

Stack memory is memory of all objects that are actively in use or will be used in the near future. Heap memory is the memory of all objects whose scope is unknown to the program. Developers control the lifetime of the objects in the heap memory and delete them when it is no longer used. Memory management is the term used to describe heap memory management. Developers write a program that creates the objects in the heap memory and deletes them when it is of no use. The developer managed memory is referred as manual memory management.
